Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-25 paper/paper.tex
Attempts at improving efficiency and adaptive threshold

Our team encoded this information as a ``clock value'' between 1 and 12 when recording it by hand. To convert \verb|principal_axis| to \verb|clock|, the sign of \(x\) and \(y\) on the principal axis are used to determine which Cartesian quadrant the fish is angles into relative to its centroid. Depending on this quadrant, we then dot product the principal axis with either \([-1,0]\), \([0,-1]\), \([1,0]\) or \([0,1]\) which correspond to 9, 6, 3 and ``0'' o'clock respectively. The resulting radian value is then converted to a polar displacement in clock value space, and added to the comparative clock value used in the dot product. This then gives the fish's clock value from 0 to \(11.\overline{9}\). Before recording as \verb|clock| in the output, the value is rounded to the nearest integer, and in the event of a 0 final result it is replaced with 12.
\subsubsection{scale and length}
\(\frac{\mathrm{pixels}}{\mathrm{inch}}\) can be calculated by measuring the distance between the digits 2 and 3 found on the ruler by \verb|detectron|. Converting this to \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) gives the \verb|scale| metadata property as reported in the output.

>>>>

Our team encoded this information as a ``clock value'' between 1 and 12 when recording it by hand. To convert \verb|principal_axis| to \verb|clock_value|, the sign of \(x\) and \(y\) on the principal axis are used to determine which Cartesian quadrant the fish is angles into relative to its centroid. Depending on this quadrant, we then dot product the principal axis with either \([-1,0]\), \([0,-1]\), \([1,0]\) or \([0,1]\) which correspond to 9, 6, 3 and ``0'' o'clock respectively. The resulting radian value is then converted to a polar displacement in clock value space, and added to the comparative clock value used in the dot product. This then gives the fish's clock value from 0 to \(11.\overline{9}\). Before recording as \verb|clock_value| in the output, the value is rounded to the nearest integer, and in the event of a 0 final result it is replaced with 12.
\subsubsection{scale and length}
\(\frac{\mathrm{pixels}}{\mathrm{inch}}\) can be calculated by measuring the distance between the digits 2 and 3 found on the ruler by \verb|detectron|. Converting this to \(\frac{\mathrm{pixels}}{\mathrm{cm}}\) gives the \verb|scale| metadata property as reported in the output.
